---
title: "Import"
author: "Zachary M. Smith"
date: "December 27, 2017"
output: html_document
---

## Import Hourly Data
```{r}
hourly.df <- file.path(rprojroot::find_rstudio_root_file(), "data_ts/historical/flows_obs/hourly_flows.zip") %>%
  unzip(exdir = file.path(rprojroot::find_rstudio_root_file(), "data_ts/historical/flows_obs/hourly_flows.csv"),
        overwrite = TRUE) %>% 
  data.table::fread(
    data.table = FALSE,
    na.strings = c("", " ", "Eqp", "#N/A", "-999999"),
    showProgress = FALSE) %>% 
  dplyr::filter(site %in% c("goose", "lfalls", "mon_jug", "por", "seneca")) %>% 
  mutate(date_time = ymd_hms(date_time)) %>% 
  dplyr::filter(!is.na(flow))
```

```{r}
hourly.df <- hourly.df %>% 
  select(date_time, site, flow) %>% 
  group_by(date_time, site) %>% 
  summarize(flow = mean(flow, na.rm = TRUE)) %>% 
  ungroup() %>%
  spread(site, flow) %>% 
  dplyr::filter(!is.na(goose) & !is.na(lfalls) & 
                  !is.na(mon_jug) & !is.na(por) & !is.na(seneca)) %>% 
  gather(site, flow, goose:seneca)
```
The area adjustment factors below account for ungaged drainage areas. They were computed using river segment areas in the CBP's Phase 5.2 watershed model. 
```{r}
hourly_adjusted.df <- hourly.df %>% 
  dplyr::mutate(flow = case_when(
    site == "por" ~ flow * 1.046,
    site == "mon_jug" ~ flow * 1.189,
    site == "goose" ~ flow * 1.164,
    site == "seneca" ~ flow * 1.270,
    TRUE ~ flow * 1
  ))
```

## Import Withdrawals
```{r}
with.df <- file.path(rprojroot::find_rstudio_root_file(), "data_ts/historical/withdrawals/withdrawals_wma_daily_mgd_1990_2017.csv") %>%
  data.table::fread(data.table = FALSE,
                    na.strings = c("", " ", "Eqp", "#N/A", "-999999")) %>% 
  dplyr::filter(!rowSums(is.na(.)) == ncol(.))
```
### Right now, must grab data from 3 "locations" to get withdrawals at all 4 WMA Potomac river intakes. Need to talk more with Sarah about date of "yesterday" withdrawal. 
```{r}
pot.wma.total.daily <- with.df %>% 
  dplyr::filter(location %in% c("Potomac River", "Potomac River at Little Falls",
                                "Potomac River at Great Falls") ) %>% 
  dplyr::group_by(measurement, date_time, units) %>% 
  dplyr::summarize(value = sum(value)) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(unique_id = "potomac_wma_total", date = as.Date(date_time),
                withdr_pot_tot_mgd = value) %>% 
  dplyr::filter(!rowSums(is.na(.)) == ncol(.)) %>%
  dplyr:: select(date, withdr_pot_tot_mgd)
```

# Don't remove for now for QAing:
```{r}
#rm(with.df, withdrawals.df, pot.total)
```

