---
title: "Import"
author: "Zachary M. Smith"
date: "December 27, 2017"
output: html_document
---

## Import Hourly Data

These data are downloaded from USGS and units are cfs, but note that tz is UTC - have to somehow incorporate this.

hourly.df has columns: date_time, site (por, lfalls, ...), flow.
```{r}
hourly.df <- file.path(rprojroot::find_rstudio_root_file(), "data_ts/historical/flows_obs/hourly_flows.csv") %>%
  data.table::fread(
    data.table = FALSE,
    na.strings = c("", " ", "Eqp", "#N/A", "-999999"),
    showProgress = FALSE) %>% 
  dplyr::filter(site %in% c("goose", "lfalls", "mon_jug", "por", "seneca")) %>% 
  mutate(date_time = ymd_hms(date_time)) %>% 
  dplyr::filter(!is.na(flow))
```

```{r}
hourly.df <- hourly.df %>% 
  select(date_time, site, flow) %>% 
  group_by(date_time, site) %>% 
  summarize(flow = mean(flow, na.rm = TRUE)) %>% 
  ungroup() %>%
  spread(site, flow) %>% 
  dplyr::filter(!is.na(goose) & !is.na(lfalls) & 
                  !is.na(mon_jug) & !is.na(por) & !is.na(seneca)) %>% 
  gather(site, flow, goose:seneca)
```
The area adjustment factors below account for ungaged drainage areas. They were computed using river segment areas in the CBP's Phase 5.2 watershed model. 
```{r}
hourly.adjusted.df <- hourly.df %>% 
  dplyr::mutate(flow = case_when(
    site == "por" ~ flow * 1.046,
    site == "mon_jug" ~ flow * 1.189,
    site == "goose" ~ flow * 1.164,
    site == "seneca" ~ flow * 1.270,
    TRUE ~ flow * 1
  ))
```

## Import Withdrawals
```{r}
with.df <- file.path(rprojroot::find_rstudio_root_file(), "data_ts/historical/withdrawals/withdrawals_wma_daily_mgd_1990_2017.csv") %>%
  data.table::fread(data.table = FALSE,
                    na.strings = c("", " ", "Eqp", "#N/A", "-999999")) %>% 
  dplyr::filter(!rowSums(is.na(.)) == ncol(.))
```
### Right now, must grab data from 3 "locations" to get withdrawals at all 4 WMA Potomac river intakes. Need to talk more with Sarah about date of "yesterday" withdrawal. Don't forget to convert mgd to cfs to match flow data. 
```{r}
pot.wma.total.daily <- with.df %>% 
  dplyr::filter(location %in% c("Potomac River", "Potomac River at Little Falls",
                                "Potomac River at Great Falls") ) %>% 
  dplyr::group_by(measurement, date_time, units) %>% 
  dplyr::summarize(value = sum(value)) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(unique_id = "potomac_wma_total", date = as.Date(date_time),
                withdr_pot_tot_mgd = value,
                withdr_pot_tot = withdr_pot_tot_mgd * 1.547) %>% 
  dplyr::filter(!rowSums(is.na(.)) == ncol(.)) %>%
  dplyr:: select(date, withdr_pot_tot)
```

```{r}
hourly.graph <- hourly.adjusted.df %>% 
#  select(site, date_time, flow) %>% 
  filter(site %in% c("lfalls", "por"),
         date_time >= "1995-01-01") %>%
  dplyr::mutate(year = year(date_time),
#         month = month(date_time, label = TRUE)) %>% 
        month = month(date_time)) %>% 
  distinct()
```
  #

```{r fig.width=10, fig.height=40}
ggplot(hourly.graph, aes(date_time, log10(flow), group = site)) +
  geom_line(aes(color = site), size = 1, alpha = 0.5) +
  scale_x_datetime(date_labels = "%b",
                   date_breaks = "1 month") +
  facet_wrap(~year, ncol = 1, scale = "free")
```
