---
title: "Import"
author: "Zachary M. Smith"
date: "December 27, 2017"
output: html_document
---

## Import Hourly Data
```{r}
hourly.df <- file.path(rprojroot::find_rstudio_root_file(), "data_ts/historical/flows_obs/hourly_flows.csv") %>%
  data.table::fread(
    data.table = FALSE,
    na.strings = c("", " ", "Eqp", "#N/A", "-999999"),
    showProgress = FALSE) %>% 
  filter(site %in% c("goose", "lfalls", "mon_jug", "por", "seneca")) %>% 
  mutate(date_time = ymd_hms(date_time)) %>% 
  filter(!is.na(flow))
```

```{r}
hourly.df <- hourly.df %>% 
  select(date_time, site, flow) %>% 
  group_by(date_time, site) %>% 
  summarize(flow = mean(flow, na.rm = TRUE)) %>% 
  ungroup() %>%
  spread(site, flow) %>% 
  filter(!is.na(goose) & !is.na(lfalls) & !is.na(mon_jug) & !is.na(por) & !is.na(seneca)) %>% 
  gather(site, flow, goose:seneca)
```

```{r}
hourly.df <- hourly.df %>% 
  mutate(flow = case_when(
    site == "por" ~ flow * 1.046,
    site == "mon_jug" ~ flow * 1.189,
    site == "goose" ~ flow * 1.164,
    site == "seneca" ~ flow * 1.270,
    TRUE ~ flow * 1
  ))
```

## Import Withdrawals
```{r}
with.df <- file.path(rprojroot::find_rstudio_root_file(), "data_ts/historical/withdrawals/withdrawals_wma_daily_mgd_1990_2017.csv") %>%
  data.table::fread(data.table = FALSE,
                    na.strings = c("", " ", "Eqp", "#N/A", "-999999")) %>% 
  dplyr::filter(!rowSums(is.na(.)) == ncol(.))
```

```{r}
pot.total <- with.df %>% 
  dplyr::filter(location == "Potomac River"#,
                #day == "yesterday",
                #measurement == "daily average withdrawals"
  ) %>% 
  dplyr::group_by(measurement, date_time, units) %>% 
  dplyr::summarize(value = sum(value)) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(unique_id = "potomac_total") %>% 
  dplyr::filter(!rowSums(is.na(.)) == ncol(.))
```

```{r}
withdrawals.df <- dplyr::bind_rows(with.df, pot.total) %>% 
  dplyr::rename(site = unique_id,
                flow = value) %>% 
  #    dplyr::mutate(date_time = as.Date(date_time, "%m/%d/%Y"))
  dplyr::mutate(date_time = as.Date(date_time, "%Y-%m-%d")) %>% 
  dplyr::filter(!stringr::str_detect(site, "usable storage|usable capacity"))
```

```{r}
withdrawals.sub <- withdrawals.df %>% 
  # Yesterday or Today??????????????????????????????????????????????????????????????????????
  dplyr::filter(measurement == "daily average withdrawals",
                day == "yesterday") %>% 
  dplyr::select(date_time, site, flow) %>% 
  tidyr::spread(site, flow) %>% 
  dplyr::mutate(withdrawals = rowSums(.[, c('WA Potomac River at Great Falls daily average withdrawals',
                                            'WA Potomac River at Little Falls daily average withdrawals',
                                            'FW Potomac River daily average withdrawals',
                                            'WSSC Potomac River daily average withdrawals')],
                                      na.rm = TRUE)) %>% 
  dplyr::select(date_time, withdrawals) %>% 
  dplyr::rename(date = date_time)
```

```{r}
rm(with.df, withdrawals.df, pot.total)
```

## Klag

### Import lag and loss parameters
To reduce number of parameters to be adjusted, just calibrate reach lags & 
losses, calculating subreach lags & losses by multiplying by frac_of_reach_length.  
!Parameter files are now: 

* k_lag_reaches.csv:  
    + reach  
    + flow_cfs  
    + reach_lag_hours  
    + reach_loss_fraction    
* k_lag_subreaches.csv:  
    + reach  
    + subreach  
    + frac_of_reach_length
    
```{r}
klag_reaches.df <- file.path(rprojroot::find_rstudio_root_file(),
                             "data/parameters/k_lag_reaches.csv") %>% 
  data.table::fread(data.table = FALSE) %>% 
  rename_all(tolower) %>% 
  mutate(reach = tolower(reach))

klag_subreaches.df <- file.path(rprojroot::find_rstudio_root_file(), "data/parameters/k_lag_subreaches.csv") %>% 
  data.table::fread(data.table = FALSE) %>% 
  rename_all(tolower) %>% 
  mutate(reach = tolower(reach),
         subreach = tolower(subreach))

klag.df <- klag_subreaches.df %>%
  dplyr::left_join(klag_reaches.df, by = "reach") %>%
  dplyr::mutate(subreach_lag = reach_lag_hours*frac_of_reach_length,
                subreach_loss = reach_loss_fraction*frac_of_reach_length)
```

```{r}
rm(klag_reaches.df, klag_subreaches.df)
```



