---
title: "Untitled"
author: "Zachary M. Smith"
date: "January 16, 2018"
output: html_document
---

---
title: "Optimization"
author: Zachary M. Smith
output: html_notebook
---

## Simple Lag K Optimization using GA package: subreach is simply POR to LFalls.
```{r}
# klag.df columns are: site, flow, ..., lag, loss
klag.df <- file.path(rprojroot::find_rstudio_root_file(),
                     "data/parameters/k_lag.csv") %>% 
  data.table::fread(data.table = FALSE) %>%
  rename_all(tolower) %>%
  mutate(site = tolower(site))
```

```{r}
hourly.df <- file.path(rprojroot::find_rstudio_root_file(),
                       "data_ts/historical/flows_obs/hourly_flows/hourly_flows.csv") %>%
  data.table::fread(
    data.table = FALSE,
    na.strings = c("", " ", "Eqp", "#N/A", "-999999"),
    showProgress = FALSE) %>% 
  filter(site %in% c("goose", "lfalls", "mon_jug", "por", "seneca")) %>% 
  mutate(date_time = ymd_hms(date_time)) %>% 
  filter(!is.na(flow))
```

```{r}
# 
source(file.path(rprojroot::find_rstudio_root_file(), "functions/variable_lagk_func.R"))
```


## Simple Test

For simple first test of GA, just predict L Falls from area-adjusted Point of Rocks, forgetting for the moment about withdrawals, and restrict time period.
```{r}
# 
start_data <- as.POSIXct("1997-04-01 00:00")
end_data <- as.POSIXct("1997-06-01 00:00")
#
hourly.adj.df <- hourly.df %>%
  dplyr::filter(date_time >= start_data, 
                date_time < end_data) %>%
  dplyr::mutate(flow = case_when(
    site == "por" ~ flow * 11560/9651, # area-adj POR flow
    TRUE ~ flow)) %>% 
  select(-agency, -timezone, -qual_code)
```

```{r}
# The function defined here, negative_rmse, will serve as 
#    the "fitness" function.
# Values of theta = c(lag, loss) will be adjusted by GA 
#     to maximize negative_rmse.
#theta <- c(lag.min, loss.min)
#theta <- lag.min
#long.df = hourly.adj.df
#vklag.df = klag.alt
negative_rmse <- function(theta, long.df, vklag.df) {
  #----------------------------------------------------------------------------
  theta.vec <- unlist(theta)
  #----------------------------------------------------------------------------
  klag.opt <- vklag.df
  #klag.opt$lag <- theta.vec
  klag.opt$lag <- theta.vec[1:(length(theta.vec) / 2)]
  klag.opt$loss <- theta.vec[(length(theta.vec) / 2 + 1):length(theta.vec)]
  #----------------------------------------------------------------------------
  pred.df <- pred_lfalls(long.df, klag.opt)
  #----------------------------------------------------------------------------
  rmse <- calc_rmse(long.df, pred.df)
  return(rmse)
}
```



## GA

```{r}
klag.alt <- klag.df %>%  
  #filter(site != "por_all") %>% 
  mutate(lag_quant = lag * 0.1,
         lag_min = lag - lag_quant,
         lag_max = lag + lag_quant,
         loss_min = -0.5,
         loss_max = 0.5)

lag.min <- klag.alt$lag_min
lag.max <- klag.alt$lag_max
loss.min <- klag.alt$loss_min
loss.max <- klag.alt$loss_max
lag.org <- klag.alt$lag
loss.org <- klag.alt$loss
```

```{r}
org.rmse <- negative_rmse(c(lag.org, loss.org), long.df = hourly.adj.df, vklag.df = klag.alt)
```

```{r}
ga.simple <- ga(type = "real-valued", fitness = negative_rmse,
               long.df = hourly.adj.df, vklag.df = klag.alt,
               min = c(lag.min, loss.min),
               max = c(lag.max, loss.max),
               run  = 20,
               maxiter = 200,
               seed = 84,  # Selected with: sample(1:100, 1)
               optim = TRUE,
               parallel = TRUE
               )
summary(ga.simple)
```

```{r}
plot(ga.simple)
```

```{r}
klag.alt  <- klag.alt  %>% 
  mutate(best_lag = ga.simple@solution[1:nrow(.)],
         best_loss = ga.simple@solution[(nrow(.) + 1):length(ga.simple@solution)],
         ga_rmse = ga.simple@fitnessValue,
         org_rmse = org.rmse)

file.dir <- paste0("ga_klag_thresholds_", format(Sys.Date(), "%m_%d_%Y"), ".csv")
data.table::fwrite(klag.alt,
                   file.path(rprojroot::find_rstudio_root_file(), "data/parameters", file.dir))

```

```{r}
org.df <- pred_lfalls(hourly.adj.df, klag.alt)
```

```{r}
klag.ga <- klag.alt %>% 
  select(site, flow, best_lag, best_loss) %>% 
  rename(lag = best_lag,
         loss = best_loss)
ga.df <- pred_lfalls(hourly.adj.df, klag.ga) %>% 
  mutate(site = if_else(site == "predicted", "ga", site)) %>% 
  filter(site == "ga")
```

```{r}
comb.df <- org.df %>% 
  filter(site %in% c("lfalls", "predicted")) %>% 
  mutate(site = if_else(site == "predicted", "original", site)) %>% 
  bind_rows(ga.df)
```

```{r}
ggplot(comb.df, aes(date_time, flow, group = site)) +
  geom_line(aes(color = site, size = site, alpha = site)) +
  scale_alpha_manual(values = c("lfalls" = 1,
                               "ga" = 0.5,
                               "original" = 0.5)) +
  scale_color_manual(values = c("lfalls" = "gray",
                               "ga" = "red",
                               "original" = "green")) +
  scale_size_manual(values = c("lfalls" = 1.2,
                               "ga" = 1,
                               "original" = 1)) +
  scale_x_datetime(date_labels = "%b",
                   date_breaks = "1 month")
```


## Create a wide df of lfalls sim and obs, and calculate some stats:

```{r}
# lagk.df <- bind_rows(hourly.df, pred.df)
lagk.results.df <- bind_rows(hourly.df, pred.df) %>%
  dplyr::filter(site %in% c("lfalls", "predicted"))
lagk.results.wide <- lagk.results.df %>%
  tidyr::spread(site, flow) %>%
  dplyr::filter(lfalls != "NA", predicted != "NA") %>%
  dplyr::rename(obs = lfalls, sim = predicted) %>%
  dplyr::mutate(lobs = log10(obs), lsim = log10(sim))
simbar <- mean(lagk.results.wide$sim)
obsbar <- mean(lagk.results.wide$obs)
lsimbar <- mean(lagk.results.wide$lsim)
lobsbar <- mean(lagk.results.wide$lobs)
lagk.results.wide <- lagk.results.wide %>%
  dplyr::mutate(se = (sim - obs)^2, 
                ss = (obs - obsbar)^2,
                ae = abs(sim - obs),
                ape = abs((sim-obs)/obs),
                se_l = (lsim - lobs)^2, 
                ss_l = (lobs - lobsbar)^2,
                ae_l = abs(lsim - lobs),
                ape_l = abs((lsim-lobs)/lobs))
mse <- mean(lagk.results.wide$se)
mss <- mean(lagk.results.wide$ss)
mae <- mean(lagk.results.wide$ae)
mape <- mean(lagk.results.wide$ape)
nse <- 1 - mse/mss
mse_l <- mean(lagk.results.wide$se_l)
mss_l <- mean(lagk.results.wide$ss_l)
mae_l <- mean(lagk.results.wide$ae_l)
mape_l <- mean(lagk.results.wide$ape_l)
nse_l <- 1 - mse_l/mss_l

```
## 
