---
title: "Optimization"
author: Zachary M. Smith
output: html_notebook
---

## Simple Lag K Optimization using GA package: subreach is simply POR to LFalls.
### Consider renaming klag.df columns to reach, subreach, ..., lag_reach, lag_subreach, ...
```{r}
# klag.df columns are: site, flow, ..., lag, loss.
#   - in this analysis we're interested in site = por_all.
klag.df <- file.path(rprojroot::find_rstudio_root_file(),
                             "data/parameters/k_lag.csv") %>% 
  data.table::fread(data.table = FALSE) %>%
  rename_all(tolower) %>%
  mutate(site = tolower(site))
```

```{r}
# 
source(file.path(rprojroot::find_rstudio_root_file(), "functions/variable_lagk_func_test.R"))
```

```{r}
date_frame <- function(start.date, end.date, seq.by = "hour") {
  data.frame(date_time = seq.POSIXt(start.date, end.date, by = seq.by))
}
```
## For simple first test of GA, just predict L Falls from area-adjusted Point of Rocks, forgetting for the moment about withdrawals, and restrict time period.
```{r}
# 
start_data <- as.POSIXct("1996-01-01 00:00")
end_data <- as.POSIXct("2000-12-01 00:00")
#
hourly.adj.df <- hourly.df %>%
  dplyr::filter(site  %in% c("por", "lfalls"),
                date_time >= start_data, 
                date_time < end_data) %>%
  dplyr::mutate(flow = case_when(
    site == "por" ~ flow * 11560/9651, # area-adj POR flow
    TRUE ~ flow * 1),
    date = as.Date(date_time))
hourly.adj.df <- left_join(hourly.adj.df, pot.wma.total.daily, by = "date") %>%
  dplyr::mutate(flow = if_else(site == "por",
                               flow - withdr_pot_tot_mgd, flow)) %>%
  select(date_time, site, flow)
```

```{r}
  # The function defined here, negative_rmse, will serve as 
  #    the "fitness" function.
  # Values of theta = c(lag, loss) will be adjusted by GA 
  #     to maximize negative_rmse.
negative_rmse <- function(theta, long.df, gage, subreach, vklag.df) {
#  negative_rmse <- function(lag, loss, long.df, gage, subreach, vklag.df) {
  # long.df = hourly.adj.df has 
  #     date_time
  #     site (lfalls, por)
  #     flow (por flow has been area-adjusted)
  # theta[1] = a lag parameter to be optimized
  # theta[2] = a loss parameter to be optimized
  # gage (site.name): gage whose data is to be lagged - will be set at "por""
  # subreach (por.lag): downstream subreach - will be set at "por_all"
  #
  # First need to change targeted lags and losses in klag.df
  # klag.opt will be like klag.df, but will have the altered lag & loss
   klag.opt <- vklag.df %>%
    dplyr::mutate(lag = if_else(site == "por_all" & flow == 10, 
                                theta[1], lag)) %>%
    dplyr::mutate(loss = if_else(site == "por_all" & flow == 10, 
                                theta[2], loss)) %>%
    dplyr::mutate(lag = if_else(site == "por_all" & flow == 500, 
                                theta[3], lag)) %>%
    dplyr::mutate(loss = if_else(site == "por_all" & flow == 500, 
                                theta[4], loss)) %>%
    dplyr::mutate(lag = if_else(site == "por_all" & flow == 2500, 
                                theta[5], lag)) %>%
    dplyr::mutate(loss = if_else(site == "por_all" & flow == 2500, 
                                theta[6], loss))
  #
  pred.df <- variable_lagk(long.df, gage, subreach, klag.opt)
  #
  # Now want to compute the rmse (try other measures of error later)
  lagk.results.df <- bind_rows(long.df, pred.df) %>%
  dplyr::filter(site %in% c("lfalls", "predicted"))
  #
  lagk.results.wide <- lagk.results.df %>%
  tidyr::spread(site, flow) %>%
  dplyr::filter(!is.na(lfalls), !is.na(predicted)) %>%
    dplyr::mutate(se = (log10(lfalls) - log10(predicted))^2)
  mse <- mean(lagk.results.wide$se)
# rmse <- sqrt(mean(lagk.results.wide$lfalls
#                  - lagk.results.wide$predicted)^2)
rmse2 <- sqrt(mse)
#answer <- list(lagk.results.wide, rmse2)
answer <- -rmse2
return(answer)
}
testlfalls <- filter(hourly.adj.df, site == "lfalls")
testpor <- filter(hourly.adj.df, site == "por")
min(testpor$flow)
quantile(testpor$flow, 0.02)
max(testpor$flow)
min(testlfalls$flow)
quantile(testlfalls$flow, 0.02)
max(testlfalls$flow)


```

## GA
```{r}
#
GAsimple <- ga(type = "real-valued", fitness = negative_rmse,
               long.df = hourly.adj.df, gage = "por", 
               subreach = "por_all", vklag.df = klag.df,
               min = c(40, -0.05, 25, -0.05, 20, -0.05), 
               max = c(60, 0.05, 45, 0.05, 30, 0.05),
               maxiter = 5)
summary(GAsimple)
```

```{r}
#

```
## Evaluate the new lags and losses from GA by calculating some stats.
### First copy in the final lags and losses from GA:
```{r}
# For reference, 
# we started with 48.0, 0.00, 30.0, 0.00, 24.0, 0.00
lags_losses <- c(50.9, -0.01, 25.8, 0.03, 23.5, 0.04)
   klag.new.df <- klag.df %>%
    dplyr::mutate(lag = if_else(site == "por_all" & flow == 10, 
                                lags_losses[1], lag)) %>%
    dplyr::mutate(loss = if_else(site == "por_all" & flow == 10, 
                                lags_losses[2], loss)) %>%
    dplyr::mutate(lag = if_else(site == "por_all" & flow == 500, 
                                lags_losses[3], lag)) %>%
    dplyr::mutate(loss = if_else(site == "por_all" & flow == 500, 
                                lags_losses[4], loss)) %>%
    dplyr::mutate(lag = if_else(site == "por_all" & flow == 2500, 
                                lags_losses[5], lag)) %>%
    dplyr::mutate(loss = if_else(site == "por_all" & flow == 2500, 
                                lags_losses[6], loss))
# 
# Now use the new lags and losses to predict flow at lfalls:
  pred.df <- variable_lagk(hourly.adj.df, "por", "por_all", klag.new.df)
#
# Compute some error stats - for full range of flows and for range of low flows:
  lagk.results.df <- bind_rows(hourly.adj.df, pred.df) %>%
  dplyr::filter(site %in% c("lfalls", "predicted"))
  #
  lagk.results.wide <- lagk.results.df %>%
  tidyr::spread(site, flow) %>%
  dplyr::filter(!is.na(lfalls), !is.na(predicted)) %>%
    dplyr::rename(obs = lfalls, sim = predicted) %>%
    dplyr::mutate(se_log = (log10(obs) - log10(sim))^2, # square error of logs
                  obs_log = log10(obs),
                  err = sim - obs, # error
                  ape = abs((sim - obs)/obs)) # absolute percent error
  mo_log <- mean(lagk.results.wide$obs_log)
  mse_log <- mean(lagk.results.wide$se_log) # mean of square errors of logs
  msx <- mean( (lagk.results.wide$obs_log - mo_log)^2 )
  nse <- 1 - mse_log/msx # Nash-Suttcliffe efficiency - a popular time series model error
  merr <- mean(lagk.results.wide$err) # mean error
  mape <- mean(lagk.results.wide$ape) # mean absolute percent error
#
# For low flows (<= 1000 cfs for now)  
  lowflow_level <- 1000
  lagk.results.low <- lagk.results.wide %>%
  dplyr::filter(obs <= lowflow_level) %>%
  dplyr::mutate(lobs = log10(obs), lsim = log10(sim))

  mo_log_low <- mean(lagk.results.low$obs_log)
  mse_log_low <- mean(lagk.results.low$se_log)
  msx_low <- mean( (lagk.results.low$obs_log - mo_log_low)^2 )
  nse_low <- 1 - mse_log_low/msx_low
  merr_low <- mean(lagk.results.low$err)
  mape_low <- mean(lagk.results.low$ape)

lagk_stats <- c(mo_log, mse_log, nse, merr, mape,
                mo_log_low, mse_log_low, nse_low, merr_low, mape_low)
lagk_stats

```
## 
