---
title: "Lag-K Assessment"
author: Zachary M. Smith
output: html_notebook
---


# Introduction

```{r, messages=FALSE}
library(tidyverse)
library(lubridate)
library(stringr)
```

# Import Data

## Import Hourly Data

```{r}
hourly.df <- file.path(rprojroot::find_rstudio_root_file(), "data_ts/historical/flows_obs/hourly_flows.csv") %>%
  data.table::fread(
    data.table = FALSE,
    na.strings = c("", " ", "Eqp", "#N/A", "-999999"),
    showProgress = FALSE) %>% 
  filter(site %in% c("goose", "lfalls", "mon_jug", "por", "seneca")) %>% 
  mutate(date_time = ymd_hms(date_time)) %>% 
  filter(!is.na(flow)) #%>% 

#mutate(flow = if_else(date_time >= as.POSIXct("1995-01-01") & date_time < as.POSIXct("1996-01-01") & site == "por", 
#                      2000000, flow))
```
# Import lag and loss parameters
To reduce number of parameters to be adjusted, just calibrate reach lags & 
losses, calculating subreach lags & losses by multiplying by frac_of_reach_length.  
!Parameter files are now:  
* k_lag_reaches.csv:  
    + reach  
    + flow_cfs  
    + reach_lag_hours  
    + reach_loss_fraction    
* k_lag_subreaches.csv:  
    + reach  
    + subreach  
    + frac_of_reach_length
```{r}
klag_reaches.df <- file.path(rprojroot::find_rstudio_root_file(), "data/parameters/k_lag_reaches.csv") %>% 
  data.table::fread(data.table = FALSE) %>% 
  rename_all(tolower) %>% 
  mutate(reach = tolower(reach))
klag_subreaches.df <- file.path(rprojroot::find_rstudio_root_file(), "data/parameters/k_lag_subreaches.csv") %>% 
  data.table::fread(data.table = FALSE) %>% 
  rename_all(tolower) %>% 
  mutate(reach = tolower(reach), subreach = tolower(subreach))
klag.df <- klag_subreaches.df %>%
  dplyr::left_join(klag_reaches.df, by = "reach") %>%
  dplyr::mutate(subreach_lag = reach_lag_hours*frac_of_reach_length,
                subreach_loss = reach_loss_fraction*frac_of_reach_length)
```

```{r}
source(file.path(rprojroot::find_rstudio_root_file(), "functions/variable_lagk_func_test.R"))
```

```{r}
date_frame <- function(start.date, end.date, seq.by = "hour") {
  
  data.frame(date_time = seq.POSIXt(start.date, end.date, by = seq.by))
}
```


```{r}
long1.df <- hourly.df
gage1 <- "por" # this is node of the hydrograph to be lagged; maybe the "head node"?
subreach1 <- "por_1"
long2.df <- hourly.df
gage2 <- "mon_jug" # this is node of the second contributing hydrograph to be lagged
subreach2 <- "monoc_1"


variable_confluence <- function(long1.df, gage1, subreach1,
                                long2.df, gage2, subreach2, klag.df) {
  g1.df <- variable_lagk(long1.df, gage1, subreach1, klag.df)
  g2.df <- variable_lagk(long2.df, gage2, subreach2, klag.df)
  final.df <- bind_rows(long2.df, g1.df, g2.df) %>% 
    group_by(date_time, site) %>% 
    summarize(flow = sum(flow)) %>% # summing the two lagged hydrographs
    ungroup()
  return(final.df)
}
```

```{r}
pred.df <- variable_confluence(hourly.df, "por", "por_1", 
                               hourly.df, "mon_jug", "monoc_1", klag.df) %>% 
  variable_confluence("predicted", "por_2",
                      hourly.df, "goose", "goose_1", klag.df) %>% 
  variable_confluence("predicted", "por_3",
                      hourly.df, "seneca", "seneca_1", klag.df) %>% 
  variable_lagk("predicted", "por_4", klag.df)
```

```{r}
lagk.df <- bind_rows(hourly.df, pred.df)
```


## Import Widthdrawl Data

```{r}
with.df <- file.path(rprojroot::find_rstudio_root_file(), "data_ts/historical/withdrawals/withdrawals_wma_daily_mgd_1990_2017.csv") %>%
  data.table::fread(data.table = FALSE,
                    na.strings = c("", " ", "Eqp", "#N/A", "-999999")) %>% 
  dplyr::filter(!rowSums(is.na(.)) == ncol(.))
```

```{r}
pot.total <- with.df %>% 
  dplyr::filter(location == "Potomac River"#,
                #day == "yesterday",
                #measurement == "daily average withdrawals"
  ) %>% 
  dplyr::group_by(measurement, date_time, units) %>% 
  dplyr::summarize(value = sum(value)) %>% 
  dplyr::ungroup() %>% 
  dplyr::mutate(unique_id = "potomac_total") %>% 
  dplyr::filter(!rowSums(is.na(.)) == ncol(.))
```

```{r}
withdrawals.df <- dplyr::bind_rows(with.df, pot.total) %>% 
  dplyr::rename(site = unique_id,
                flow = value) %>% 
  #    dplyr::mutate(date_time = as.Date(date_time, "%m/%d/%Y"))
  dplyr::mutate(date_time = as.Date(date_time, "%Y-%m-%d")) %>% 
  dplyr::filter(!stringr::str_detect(site, "usable storage|usable capacity"))
```


```{r}
withdrawals.sub <- withdrawals.df %>% 
  # Yesterday or Today??????????????????????????????????????????????????????????????????????
  dplyr::filter(measurement == "daily average withdrawals",
                day == "yesterday") %>% 
  dplyr::select(date_time, site, flow) %>% 
  tidyr::spread(site, flow) %>% 
  dplyr::mutate(withdrawals = rowSums(.[, c('WA Potomac River at Great Falls daily average withdrawals',
                                            'WA Potomac River at Little Falls daily average withdrawals',
                                            'FW Potomac River daily average withdrawals',
                                            'WSSC Potomac River daily average withdrawals')],
                                      na.rm = TRUE)) %>% 
  dplyr::select(date_time, withdrawals) %>% 
  dplyr::rename(date = date_time)
```

## Join Lag-K with Widthdrawl Data

```{r}
lagk.df <- lagk.df %>% 
  tidyr::separate(date_time, into = c("date", "time"), convert = TRUE,
                  sep = " ", remove = FALSE) %>% 
  dplyr::mutate(date = as.Date(date)) %>% 
  dplyr::left_join(withdrawals.sub, by = "date") %>% 
  dplyr::select(-date, -time) %>% 
  dplyr::mutate(flow = if_else(site == "predicted" & !is.na(withdrawals),
                               flow - withdrawals,
                               flow)) %>% 
  dplyr::select(-withdrawals)
```


```{r}
# For the time being lets not remove these - to facilitate QA'ing:
# rm(hourly.df, klag.df, pot.total, pred.df, with.df, withdrawals.df, withdrawals.sub, date_frame, variable_confluence, variable_lagk)
```




